Fourmile Calibrations and Output

### 2025-04-04 fourmile_output_dec2024.Rmd
changed pbias and kge plots by categories

# need to make separate plots bc can't put boxplots in margins for facet wrap
grid_kge_plot <- flow_plot_updated %>%
  filter(source == 'grid') %>% 
ggplot(., aes(x = year_excluded, 
              y = year, fill = 
                kge_revise)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "mako", 
                       name = "KGE", 
                       direction = -1) +
  geom_text(aes(label = sprintf("%.2f", 
                                kge_revise)), 
            color = "grey", 
            size = 2.5) +
  theme_bw(base_size=20) +
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1)) +
  labs(y = "Year",
       x='Year Excluded') +
  # facet_wrap(~source,
  #            scales = 'free_x',
  #            labeller = as_labeller(c("grid" = "Gridded", 
  #                                     "statn" = "Station"))) +
  theme(
    axis.text.x = element_text(angle = 45, 
                               hjust = 1),
    legend.position = 'none',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(.75, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black")
  )

grid_kge_plot

#003f5c
#58508d
#bc5090
#ff6361
#ffa600

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid.png',
       dpi=600,
       width = 10,
       height = 6)

@@

flow_plot_updated <- flow_plot_updated %>%
  mutate(kge_revise_bins = cut(kge,
                               breaks = c(-Inf, 0, 0.25, 0.5, 0.75, 1),
                               include.lowest = TRUE,
                               labels = c("< 0", "0-0.25", "0.25-0.5", "0.5-0.75", "0.75-1")))

grid_kge_plot <- flow_plot_updated %>%
  filter(source == 'grid') %>% 
ggplot(., aes(x = year_excluded, 
              y = year, 
              fill = kge_revise_bins)) +
  geom_tile(color = "white") +
  # scale_fill_manual(values = color_palette) +
paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
  geom_text(aes(label = sprintf("%.2f", 
                                kge)), 
            color = "black", 
            size = 3) +
  theme_bw(base_size=20) +
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1)) +
  labs(y = "Year",
       x='Year Excluded',
       fill = 'KGE') +
  theme(
    axis.text.x = element_text(angle = 45, 
                               hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(.75, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 0, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  ) + ggtitle('a. Gridded')

grid_kge_plot

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid_basic.png',
       dpi=600,
       width = 10,
       height = 6)

# mean_kge <- mean(flow_plot_updated$kge, na.rm = TRUE)
# 
# # Boxplot with mean line
# boxplot_x <- flow_plot_updated %>%
#   filter(source == "grid") %>%
#   ggplot(aes(x=source, y = kge)) +
#   geom_hline(yintercept = mean_kge, color = "black", linetype = "dashed", size = 0.5) +
#   geom_boxplot(outliers=F, fill = "grey", color = "black") +
#   theme_bw(base_size=16) +
#   theme(
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     strip.background = element_blank(),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     axis.title.y = element_blank(),
#     axis.title.x = element_blank(),
#     axis.text.x = element_blank(),
#     axis.ticks.x = element_blank(),
#     plot.margin = margin(t = 10, r = 5, b = 76, l = 5)  # Adjust margins if necessary
#   ) +
#    scale_y_continuous(position = "right") 
# 
# boxplot_x
# 
# plot_grid(grid_kge_plot,boxplot_x, ncol = 2, 
#           rel_widths = c(3, 0.75))
# 
# 
# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid.png',
#        dpi=600,
#        width = 10,
#        height = 6)
# 
# ######
# 
# boxplot_yrex <- flow_plot_updated %>%
#   filter(source == "grid") %>%
#   ggplot(aes(x=year_excluded, y = kge)) +
#   geom_boxplot(outliers=F, fill = "grey", 
#                color = "black",
#                width = 0.5) +
#   theme_bw(base_size=20) +
#   labs(y= 'KGE') +
#   theme(
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     strip.background = element_blank(),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     #axis.title.y = element_blank(),
#     axis.title.x = element_blank(),
#     axis.text.x = element_blank(),
#     axis.ticks.x = element_blank(),
#     plot.margin = margin(t = 10, r = 10, b = 0, l = 24)  # Adjust margins if necessary
#   )
#   
# boxplot_yrex
# 
# plot_grid(NULL, boxplot_yrex, NULL, grid_kge_plot, ncol = 1,
#            rel_heights = c(0.1, 1, -0.00005, 2))
# 
# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid_test.png',
#        dpi=600,
#        width = 10,
#        height = 6)

statn_kge_plot <- flow_plot_updated %>%
  filter(source == 'statn') %>% 
ggplot(., aes(x = year_excluded, 
              y = year, 
              fill = kge_revise_bins)) +
  geom_tile(color = "white") +
  facet_wrap(~source) +
  # scale_fill_manual(values = color_palette) +
paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
  geom_text(aes(label = sprintf("%.2f", 
                                kge)), 
            color = "black", 
            size = 3) +
  theme_bw(base_size=20) +
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1)) +
  labs(y = "Year",
       x='Year Excluded',
       fill = 'KGE') +
  theme(
    axis.text.x = element_text(angle = 45, 
                               hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(.75, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt"),
    # axis.title.y = element_blank(),
    # axis.text.y = element_blank(),
    # axis.ticks.y = element_blank()
  )

statn_kge_plot

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_statn_basic.png',
       dpi=600,
       width = 10,
       height = 6)

@@

@@

both_pbias_plot <- flow_plot_updated %>%
  ggplot(., aes(x = year_excluded, 
              y = year, 
              fill = pbias)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
  #paletteer::scale_fill_paletteer_c("ggthemes::Gold-Purple Diverging") +
  #paletteer::scale_fill_paletteer_c("grDevices::Red-Green") +
  #paletteer::scale_fill_paletteer_c("grDevices::Purple-Green") +
  paletteer::scale_fill_paletteer_c("grDevices::Green-Brown") +
  #paletteer::scale_fill_paletteer_c("grDevices::Earth") +
  geom_text(aes(label = sprintf("%.2f", 
                                pbias)), 
            color = "black", 
            size = 2.75) +
  theme_bw(base_size=18) +
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1)) +
  labs(y = "Year",
       x='Year excluded',
       fill = 'Pbias') +
  theme(
    axis.text.x = element_text(angle = 45, 
                               hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(.75, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt"),
    # axis.title.y = element_blank(),
    # axis.text.y = element_blank(),
    # axis.ticks.y = element_blank()
  )

@@

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic.png',
       dpi=600,
       width = 10,
       height = 6)

>>>>

# # need to make separate plots bc can't put boxplots in margins for facet wrap
# grid_kge_plot <- flow_plot_updated %>%
#   filter(source == 'grid') %>% 
# ggplot(., aes(x = year_excluded, 
#               y = year, fill = 
#                 kge_revise)) +
#   geom_tile(color = "white") +
#   scale_fill_viridis_c(option = "mako", 
#                        name = "KGE", 
#                        direction = -1) +
#   geom_text(aes(label = sprintf("%.2f", 
#                                 kge_revise)), 
#             color = "grey", 
#             size = 2.5) +
#   theme_bw(base_size=20) +
#   theme(axis.text.x = element_text(angle = 45, 
#                                    hjust = 1)) +
#   labs(y = "Year",
#        x='Year Excluded') +
#   # facet_wrap(~source,
#   #            scales = 'free_x',
#   #            labeller = as_labeller(c("grid" = "Gridded", 
#   #                                     "statn" = "Station"))) +
#   theme(
#     axis.text.x = element_text(angle = 45, 
#                                hjust = 1),
#     legend.position = 'none',
#     legend.text = element_text(size = 14),
#     legend.title = element_text(size = 14),
#     legend.key.width = unit(.75, "cm"),
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     strip.background = element_blank(),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black")
#   ) 
# 
# grid_kge_plot
# 
# 
# 
# #003f5c
# #58508d
# #bc5090
# #ff6361
# #ffa600
# 
# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid.png',
#        dpi=600,
#        width = 10,
#        height = 6)

@@

flow_plot_updated <- flow_plot_updated %>%
  mutate(kge_revise_bins = cut(kge,
                               breaks = c(-Inf, 0.2, 0.4, 0.6, 0.8, 1),
                               include.lowest = TRUE,
                               labels = c("< 0.0", "0.2-0.4", "0.4-0.6", "0.6-0.8", "> 0.8")))

# grid_kge_plot <- flow_plot_updated %>%
#   filter(source == 'grid') %>% 
# ggplot(., aes(x = year_excluded, 
#               y = year, 
#               fill = kge_revise_bins)) +
#   geom_tile(color = "white") +
#   # scale_fill_manual(values = color_palette) +
# paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
#   geom_text(aes(label = sprintf("%.2f", 
#                                 kge)), 
#             color = "black", 
#             size = 3) +
#   theme_bw(base_size=20) +
#   theme(axis.text.x = element_text(angle = 45, 
#                                    hjust = 1)) +
#   labs(y = "Year",
#        x='Year Excluded',
#        fill = 'KGE') +
#   theme(
#     axis.text.x = element_text(angle = 45, 
#                                hjust = 1),
#     legend.position = 'bottom',
#     legend.text = element_text(size = 14),
#     legend.title = element_text(size = 14),
#     legend.key.width = unit(.75, "cm"),
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     strip.background = element_blank(),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     plot.margin = margin(t = 0, r = 10, b = 10, l = 10),
#     legend.margin = margin(t = -8, b = -4, unit = "pt")
#   ) + ggtitle('a. Gridded')
# 
# grid_kge_plot
# 
# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid_basic.png',
#        dpi=600,
#        width = 10,
#        height = 6)

# mean_kge <- mean(flow_plot_updated$kge, na.rm = TRUE)
# 
# # Boxplot with mean line
# boxplot_x <- flow_plot_updated %>%
#   filter(source == "grid") %>%
#   ggplot(aes(x=source, y = kge)) +
#   geom_hline(yintercept = mean_kge, color = "black", linetype = "dashed", size = 0.5) +
#   geom_boxplot(outliers=F, fill = "grey", color = "black") +
#   theme_bw(base_size=16) +
#   theme(
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     strip.background = element_blank(),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     axis.title.y = element_blank(),
#     axis.title.x = element_blank(),
#     axis.text.x = element_blank(),
#     axis.ticks.x = element_blank(),
#     plot.margin = margin(t = 10, r = 5, b = 76, l = 5)  # Adjust margins if necessary
#   ) +
#    scale_y_continuous(position = "right") 
# 
# boxplot_x
# 
# plot_grid(grid_kge_plot,boxplot_x, ncol = 2, 
#           rel_widths = c(3, 0.75))
# 
# 
# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid.png',
#        dpi=600,
#        width = 10,
#        height = 6)
# 
# ######
# 
# boxplot_yrex <- flow_plot_updated %>%
#   filter(source == "grid") %>%
#   ggplot(aes(x=year_excluded, y = kge)) +
#   geom_boxplot(outliers=F, fill = "grey", 
#                color = "black",
#                width = 0.5) +
#   theme_bw(base_size=20) +
#   labs(y= 'KGE') +
#   theme(
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     strip.background = element_blank(),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     #axis.title.y = element_blank(),
#     axis.title.x = element_blank(),
#     axis.text.x = element_blank(),
#     axis.ticks.x = element_blank(),
#     plot.margin = margin(t = 10, r = 10, b = 0, l = 24)  # Adjust margins if necessary
#   )
#   
# boxplot_yrex
# 
# plot_grid(NULL, boxplot_yrex, NULL, grid_kge_plot, ncol = 1,
#            rel_heights = c(0.1, 1, -0.00005, 2))
# 
# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid_test.png',
#        dpi=600,
#        width = 10,
#        height = 6)
# 
# statn_kge_plot <- flow_plot_updated %>%
#   filter(source == 'statn') %>% 
# ggplot(., aes(x = year_excluded, 
#               y = year, 
#               fill = kge_revise_bins)) +
#   geom_tile(color = "white") +
#   facet_wrap(~source) +
#   # scale_fill_manual(values = color_palette) +
# paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
#   geom_text(aes(label = sprintf("%.2f", 
#                                 kge)), 
#             color = "black", 
#             size = 3) +
#   theme_bw(base_size=20) +
#   theme(axis.text.x = element_text(angle = 45, 
#                                    hjust = 1)) +
#   labs(y = "Year",
#        x='Year Excluded',
#        fill = 'KGE') +
#   theme(
#     axis.text.x = element_text(angle = 45, 
#                                hjust = 1),
#     legend.position = 'bottom',
#     legend.text = element_text(size = 14),
#     legend.title = element_text(size = 14),
#     legend.key.width = unit(.75, "cm"),
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     strip.background = element_blank(),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
#     legend.margin = margin(t = -8, b = -4, unit = "pt"),
#     # axis.title.y = element_blank(),
#     # axis.text.y = element_blank(),
#     # axis.ticks.y = element_blank()
#   )
# 
# statn_kge_plot
# 
# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_statn_basic.png',
#        dpi=600,
#        width = 10,
#        height = 6)

@@

#####################
kgeCats <- flow_plot_updated %>%
  mutate(pbiasCat = case_when(
    abs(pbias) < 10 ~ 'Very good',
    abs(pbias) >= 10 & abs(pbias) < 15 ~ 'Good',
    abs(pbias) >= 15 & abs(pbias) < 25 ~ 'Satisfactory',
    abs(pbias) >= 25 ~ 'Unsatisfactory'),
    pbiasCat = factor(pbiasCat, levels = c("Unsatisfactory", 
                                           "Satisfactory", 
                                           "Good", 
                                           "Very good")))

both_pbias_plot <- pbiasCats %>%
  ggplot(aes(x = year_excluded, 
             y = year, 
             fill = pbiasCat)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
  # paletteer::scale_fill_paletteer_c(
  #   "grDevices::Green-Brown",
  #   limits = c(-max_abs, max_abs),
  #   oob = scales::squish
  # ) +
  paletteer::scale_fill_paletteer_d("calecopal::lupinus") +
  geom_text(aes(label = sprintf("%.2f", pbias)), 
            color = "black", 
            size = 2.75) +
  theme_bw(base_size=18) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(1, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  ) +
  labs(y = "Year",
       x = 'Year excluded',
       fill = '% bias')

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_cats.png',
       dpi=600,
       width = 10,
       height = 6)

@@

# both_pbias_plot <- flow_plot_updated %>%
#   ggplot(., aes(x = year_excluded, 
#               y = year, 
#               fill = pbias)) +
#   geom_tile(color = "white") +
#   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
#   #paletteer::scale_fill_paletteer_c("ggthemes::Gold-Purple Diverging") +
#   #paletteer::scale_fill_paletteer_c("grDevices::Red-Green") +
#   #paletteer::scale_fill_paletteer_c("grDevices::Purple-Green") +
#   paletteer::scale_fill_paletteer_c("grDevices::Green-Brown") +
#   #paletteer::scale_fill_paletteer_c("grDevices::Earth") +
#   geom_text(aes(label = sprintf("%.2f", 
#                                 pbias)), 
#             color = "black", 
#             size = 2.75) +
#   theme_bw(base_size=18) +
#   theme(axis.text.x = element_text(angle = 45, 
#                                    hjust = 1)) +
#   labs(y = "Year",
#        x='Year excluded',
#        fill = 'Pbias') +
#   theme(
#     axis.text.x = element_text(angle = 45, 
#                                hjust = 1),
#     legend.position = 'bottom',
#     legend.text = element_text(size = 14),
#     legend.title = element_text(size = 14),
#     legend.key.width = unit(.75, "cm"),
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     strip.background = element_blank(),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
#     legend.margin = margin(t = -8, b = -4, unit = "pt"),
#     # axis.title.y = element_blank(),
#     # axis.text.y = element_blank(),
#     # axis.ticks.y = element_blank()
#   )
# 
# both_pbias_plot
# 
# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic.png',
#        dpi=600,
#        width = 10,
#        height = 6)

# Compute max absolute value for symmetric limits
# put pbias into categories
pbiasCats <- flow_plot_updated %>%
  mutate(pbiasCat = case_when(
    abs(pbias) < 10 ~ 'Very good',
    abs(pbias) >= 10 & abs(pbias) < 15 ~ 'Good',
    abs(pbias) >= 15 & abs(pbias) < 25 ~ 'Satisfactory',
    abs(pbias) >= 25 ~ 'Unsatisfactory'),
    pbiasCat = factor(pbiasCat, levels = c("Unsatisfactory", 
                                           "Satisfactory", 
                                           "Good", 
                                           "Very good")))

both_pbias_plot <- pbiasCats %>%
  ggplot(aes(x = year_excluded, 
             y = year, 
             fill = pbiasCat)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
  # paletteer::scale_fill_paletteer_c(
  #   "grDevices::Green-Brown",
  #   limits = c(-max_abs, max_abs),
  #   oob = scales::squish
  # ) +
  paletteer::scale_fill_paletteer_d("calecopal::lupinus") +
  #paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
  geom_text(aes(label = sprintf("%.2f", pbias)), 
            color = "black", 
            size = 2.75) +
  theme_bw(base_size=18) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(1, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  ) +
  labs(y = "Year",
       x = 'Year excluded',
       fill = '% bias')

@@

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_cats.png',
       dpi=600,
       width = 10,
       height = 6)

# max_abs <- max(abs(flow_plot_updated$pbias), na.rm = TRUE)
# 
# both_pbias_plot <- flow_plot_updated %>%
#   ggplot(aes(x = year_excluded, 
#              y = year, 
#              fill = pbias)) +
#   geom_tile(color = "white") +
#   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
#   paletteer::scale_fill_paletteer_c(
#     "grDevices::Green-Brown",
#     limits = c(-max_abs, max_abs),
#     oob = scales::squish
#   ) +
#   geom_text(aes(label = sprintf("%.2f", pbias)), 
#             color = "black", 
#             size = 2.75) +
#   theme_bw(base_size=18) +
#   theme(
#     axis.text.x = element_text(angle = 45, hjust = 1),
#     legend.position = 'bottom',
#     legend.text = element_text(size = 14),
#     legend.title = element_text(size = 14),
#     legend.key.width = unit(2, "cm"),
#     panel.grid = element_blank(),
#     panel.background = element_rect(fill = "white"),
#     strip.background = element_blank(),
#     text = element_text(color = "black"),
#     axis.title = element_text(color = "black"),
#     axis.text = element_text(color = "black"),
#     plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
#     legend.margin = margin(t = -8, b = -4, unit = "pt")
#   ) +
#   labs(y = "Year",
#        x = 'Year excluded',
#        fill = 'Pbias')
# 
# both_pbias_plot

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic_0center.png',
       dpi=600,
       width = 10,
       height = 6)
